Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-22 latex/comp_or.tex
Paper Comp OR update

\bgroup
\def\arraystretch{1.2}
\begin{table}[H]
	\centering
	\small
	\begin{tabular}{MT}
		&Informally, ACLP+RPDP can be summarized as follows:\\
		\midrule
		max &  (items score sum) / (tour cost) of picked up and delivered items on a tour  \\
		\midrule
s.t.    & Along a tour, the set of unvisited nodes is updated. \\
		& In each node, an item may be included in at most one pallet.\\		
		& In each node, consolidated items are composed of items with the same destination. \\
		& Weight, volume and score of a consolidated item are the corresponding sum of their components.\\
		& Consolidated items remain on board until their destinations.\\	
		& Consolidated items can only be included in the same pallet if their destinations are the same.\\
		& Only items destined for the remaining nodes can be loaded.  \\
		& The lateral and longitudinal torques must be within the operational range of the aircraft.\\
		& Weight and volume limitations of pallets must be respected.\\
		& The total weight must be less than the aircraft payload or the total pallet capacity, whichever is the lowest.\\	
		& {\bf The pallets destined for the next node of the tour should be put as near as possible to the cargo ramp door (our inclusion)}.\\
		& {\bf The items allocated to each pallet should be submitted to a 3D packing procedure (our inclusion)}.\\				
		\midrule
	\end{tabular}
	\normalsize
\end{table}
\egroup

>>>>

\bgroup
\def\arraystretch{1.2}
\begin{table}[H]
	\centering
	\small
	\begin{tabular}{MT}
		&Informally, ACLP+RPDP can be summarized as follows:\\
		\midrule
		max &  (items score sum) / (tour cost) of picked up and delivered items on a tour  \\
		\midrule
s.t.    & Along a tour, the set of unvisited nodes is updated. \\
		& In each node, an item may be included in at most one pallet.\\		
		& In each node, consolidated items are composed of items with the same destination. \\
		& Weight, volume and score of a consolidated item are the corresponding sum of their components.\\
		& Consolidated items remain on board until their destinations.\\	
		& Consolidated items can only be included in the same pallet if their destinations are the same.\\
		& Only items destined for the remaining nodes can be loaded.  \\
		& The lateral and longitudinal torques must be within the operational range of the aircraft.\\
		& Weight and volume limitations of pallets must be respected.\\
		& The total weight must be less than the aircraft payload or the total pallet capacity, whichever is the lowest.\\	
		& {\bf The pallets destined for the next node of the tour should be put as near as possible to the cargo ramp door (this work)}.\\
		& {\bf The items allocated to each pallet should be submitted to a 3D packing procedure (this work)}.\\				
		\midrule
	\end{tabular}
	\normalsize
\end{table}
\egroup
